On Secure Delegation of SampBQP with a Classical Client

### 2020-02-28 bqp.tex
Make editorial pass at BQP

@@

\def\bzrep{\mathsf{blind, 0, rep}}
\nc{\Pibzrep}{\ensuremath{\Pi_\bzrep}}

@@

In this subsection we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
\begin{thm}
	\label{thm:QPIP0BQP}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
\Ethan{Write outline here; highlight key ideas/steps}
We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.
We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{FOCS:Mahadev18a}, which is in turn taken from \cite{mf16}.

@@

Now we state our construction of blind QPIP 1 for BQP by compiling $\PiMF$ using $\QHE$:

\Ethan{TODO Rewrite this}

@@

	We define $\PMFstar$ to first generate
	$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
	and
	$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
	It then runs $\sigma\leftarrow\cPblind{1}(pk, ct_x)$
	Finally, it decrypts
	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
	and sends it to $\VMF$ qubit-by-qubit.

@@

\Ethan{Just move \protoref{urmila4} here; that's Urmila's 4 rounds protocol.
Or just move that entire subsection here really.}

\Ethan{TODO Below is copied from google docs; fix phrasing later}

Finally, we prove \cref{thm:QPIP0BQP}.
We use Mahadev's measurement protocol from \cite{FOCS:Mahadev18a} which can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol.
The resulting protocol $\Pibz$ is a constant-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$ and negligible completeness.

In order to prove blindness, we give a high-level overview of the compiliation results.
\Ethan{Need to discuss about this}

@@

\begin{thm}
	$\Pibz$ has negligible completeness error. Its soundness error is negligibly close to $\frac{3}{4}$.
\end{thm}
\begin{proof}
	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into a $\QPIP_0$ in a similar way and obtains this completeness and soundness.
	The proof uses that $\PiMF$ is one-round $\QPIP_1$ with only $X$ and $Z$ measurements on the verifier's side, with negligible completeness and soundness errors.
	$\Piblind$ is two-rounds, but we can treat the verifier's first message as additional classical public inputs, and apply the same logic to the second round.

@@

\begin{thm}[from \cite{parallelrep, alagic2019twomessage}]
	One can repeat $\PiMah$ in parallel to obtain negligible completeness and soundness errors. \Ethan{Something doesn't seem right...}
\end{thm}

@@

\Ethan{TODO PROOFREAD ME}

Our results for $\BQP$ can be generalized to $\FBQP$.

Let $f\in\FBQP$.
For any input $x\in\set{0, 1}^*$, define $f_i(x)$ to be the $i$-th bit of $f(x)$.
For $i\in\bbN, b\in\set{0,1}$, define the language $L_{i, b}=\set{x:f_i(x)=b}$.
Furthermore, define $\cL$ to be the collection of these languages: $\cL = \set{L_{i, b}: i\in[m], b\in\set{0, 1}}$.

\begin{protocol}{Blind and verifiable $\QPIP_0$ protocol $\Pi_{\FBQP}$ for $\FBQP$ language $L$}
	\label{proto:QPIP0FBQP}
	Input: $x\in\set{0, 1}^n$

	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how?}
	\begin{enumerate}
		\item Run $\Pibzrep$ for all $L\in\cL$ in parallel using input $x$.
		\item The verifier gets outputs $v_{i, b}\in\set{acc, rej}$.
			If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.
			Otherwise, define $y_i = b$ where $v_{i, b}=acc$. This gives $y\in\set{0,1}^m$.
			The verifier accepts and outputs $y$.
	\end{enumerate}
\end{protocol}

\begin{theorem}
	$\Pi_{\FBQP}$ has negligible completeness and soundness, and is blind.
\end{theorem}
\begin{prf}
	Completeness is follows by inspection.
	Blindness follows because the executions of \cref{proto:repQPIP0BQP} are blind.

@@

	By union bound over all output bits, the soundness of \cref{proto:QPIP0FBQP} is then
	$\sum_{i=1}^m \varepsilon_i$
	which is clearly negligible.
\end{prf}

>>>>

\def\MFZ{\mathsf{MFZ}}
\nc{\PiMFZ}{\ensuremath{\Pi_\MFZ}}
\def\MFZrep{\mathsf{MFZrep}}
\nc{\PiMFZrep}{\ensuremath{\Pi_\MFZrep}}

@@

\def\bzrep{\mathsf{blind, 0, rep}}
\nc{\Pibzrep}{\ensuremath{\Pi_\bzrep}}
\nc{\Vbzrep}{\ensuremath{V_\bzrep}}
\nc{\Pbzrep}{\ensuremath{P_\bzrep}}

@@

In this subsection we present our constant-round blind delegation protocol for $\BQP$.
We'll construct said protocol piece by piece, starting with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16}.
\Ethan{TODO finish outline and highlights}

@@

Now we state our construction of blind $\QPIP_1$ for $\BQP$:

@@

	We define $\PMFstar$ to first generate
	$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
	and
	$ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
	It then runs $\sigma\leftarrow\cPblind{1}(pk, ct_x)$.
	Finally, it decrypts
	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
	and sends it to $\VMF$ qubit-by-qubit.

@@

\Ethan{Formally introduce \protoref{urmila4} (measurement protocol) earlier?}

Next, we make the verifier completely classical by using \protoref{urmila4} from \cite{FOCS:Mahadev18a}.
It was originally used to compile $\PiMF$ into $\PiMFZ$ that is $\QPIP_0$. \Ethan{Say a bit more?}
It can however be applied to any $\QPIP_1$ protocol with $X$ and $Z$ measurement and negligible completeness and soundness errors.

We give a high-level overview of the compiliation results.

@@

\begin{thm}
	$\Pibz$ has negligible completeness error. Its soundness error is negligibly close to $\frac{3}{4}$.
\end{thm}
\begin{proof}
	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into a $\QPIP_0$ in a similar way and obtains this completeness and soundness.
	Its proof uses only that $\PiMF$ is $\QPIP_1$ with only $X$ and $Z$ measurements on the verifier's side, with negligible completeness and soundness errors.
	So the same logic applies here.

@@

\begin{thm}[from \cite{parallelrep, alagic2019twomessage}]
	\label{thm:MFZrep}
	$\PiMFZ$ can be repeat in parallel, obtaining $\PiMFZrep$ that has negligible completeness and soundness errors.
\end{thm}

Again, the same proof logic in \cref{thm:MFZrep} applies here. We simply repeat $\Pibz$ in parallel to get $\Pibzrep$ that is what we wanted in \cref{thm:QPIP0BQP}.

\begin{thm}
	\label{thm:QPIP0BQP}
	$\Pibzrep$ is a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

@@

Our results for $\BQP$ can be generalized to $\FBQP$ as follows:

\begin{protocol}{Blind and verifiable $\QPIP_0$ protocol $\Pi_{\FBQP}$ for $f\in\FBQP$}
	\label{proto:QPIP0FBQP}
	Verifier's input: $x\in\set{0, 1}^n$

	Public input: $f$

	Let $m=\abs{f(x)}$; we assume without loss of generality that it depends only on $n$ and can be efficiently computed classically.
	Denote the $i$-th bit of $f(x)$ as $f_i(x)$.
	For $i\in\bbN, b\in\set{0,1}$, define the $\BQP$ language $L_{i, b}=\set{s\in\set{0,1}^* : f_i(s)=b}$.
	\begin{enumerate}
		\item For all $i\in[m], b\in\set{0, 1}$ in parallel, the verifier and the prover run $(\Pbzrep, \Vbzrep(x))$ for $L_{i, b}$.
		\item The verifier gets outputs $v_{i, b}\in\set{acc, rej}$.
			If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.
			Otherwise, define $y\in\set{0,1}^m$ s.t. $y_i = b$ where $v_{i, b}=acc$,
			The verifier accepts and outputs $y$.
	\end{enumerate}
\end{protocol}

\begin{theorem}
	$\Pi_{\FBQP}$ has negligible completeness and soundness, and is blind.
\end{theorem}
\begin{prf}
	Completeness follows by inspection.
	Blindness follows because the executions of $\Pibzrep$ are blind.

@@

	By union bound over all output bits, the soundness of $\Pi_{\FBQP}$ is then
	$\sum_{i=1}^m \varepsilon_i$
	which is clearly negligible.
\end{prf}
